### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@ab58068f48cf349c47594dae2efced6b1f0a50fd 🚀

Neutral landscapes are increasingly used in ecological and evolutionary
studies over space to provide a null expectation .

@@

This software can generate neutral landscapes using twenty different
methods.

@@

@@

\textbf{Fig 2}: Benchmark comparison of all of methods in each of the
three languages

>>>>

Neutral landscapes are increasingly used in ecological and evolutionary
studies to provide a null expectation of the variance of a given metric
over space.

Wide range of disciplines: landscape genetics to biogeography.

@@

This software can generate neutral landscapes using several methods,
enables masking and works with other julia packages.

@@

\hypertarget{interoperability}{%
\subsection{Interoperability}\label{interoperability}}

Ease of use with other julia packages

Mask of neutral variable masked across quebec in 3 lines.

@@

It's fast. As the scale and resolution of raster data increases, neutral
models must be able to scale to match those data dimensions.

Here we provide two benchmark tests.

First a comparison of the speed variety of methods from each
\texttt{NeutralLandscapes.jl}, \texttt{NLMR}, and \texttt{nlmpy}.

Second we compare these performance of each of these software packages
as rasters become larger. We show that \texttt{Julia} even outperforms
the \texttt{NLMR} via C++ implemention of a particularly slow neutral
landscape method (midpoint displacement).

\textbf{Fig 2}: Benchmark comparison of selected methods in each of the
three languages

\textbf{Fig 3} scale comparison

\begin{figure}
\centering
\includegraphics{}
\caption{Comparison of speed of generating a midpoint displacement
neutral landscape (y-axis) against raster size (measured as length of
the size of a square raster, x-axis)}
\end{figure}
